Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2013-01-22 text/paper/paper3.tex
paper 3 - reworked up to discussion, conclusion missing

\begin{abstract}
  \begin{itemize}
  \item What is needed to complement the picture is data from a
    verification experiment that is as independent as possible of
    potentially conflating properties of the pictorial material and
    that is nonetheless sensitive enough to detect local readings even
    if they are dispreferred.
  \end{itemize}

\end{abstract}

@@

@@

Consequently, the \mymark{Gricean recipe}
\citep[c.f.][]{Geurts2010:Quantity-Implic} for deriving a simple
scalar inference like that in (\ref{bsp:Plain-SI-Implicature}) from an
utterance of (\ref{bsp:Plain-SI-Target}) is as follows: if the issue
whether Hans solved only some or all of the problems is relevant, then
a cooperative and knowledgable speaker would utter
(\ref{bsp:Plain-SI-Alternative}) if in a position to do so; hence, one
of the most natural explanations of why such a speaker has not uttered
(\ref{bsp:Plain-SI-Alternative}), but only (\ref{bsp:Plain-SI-Target})
is that she is uncertain of whether (\ref{bsp:Plain-SI-Alternative})
is true; but on the assumption that she is knowledgeable (competent,
opinionated, informed \dots) it follows that
(\ref{bsp:Plain-SI-Implicature}) should in fact be true.\fn{We are
  glossing here somewhat swiftly over the more nuanced details of the
  derivation of implicatures targeting the speaker's epistemic state
  \citep[e.g.][]{Gazdar1979:Pragmatics:-Imp,Soames1982:How-Presupposit},
  as this is not crucially relevant for the issues we are interested
  in here.}\textsuperscript{,}\dn{do we need to enlarge on epistemic
  implicatures?}

@@

Taking stock, traditionalism, conventionalism and grammaticalism
predict different patterns of availability and preference for \as- and
\es-sentences. Most notably, traditionalism does not predict local
readings for \es-sentences to be available, while conventionalism does
not predict any global readings to be available. Grammaticalism
predicts that all readings are available, but, given the strongest
meaning hypothesis, also comes with a clear indication of preference:
literal meanings are dispreferred. All predictions are summarized in
Table~\ref{tab:predictions}.

@@

\section{The Intonational Markedness Hypothesis}
\label{sec:inton-mark-hypoth}

Although traditionalism does not of itself predict local readings to
be available, many authors who adhere to a traditionalist position
acknowledge that local readings are available if and only if the
embedded scalar item is intonationally marked by contrastive stress
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Scalar-expressi}. This
is taken to be continuous with other cases where pragmatic enrichments
can take scope under logical operators if and only if the relevant
focal accent is present (\ref{bsp:Stress}).

\begin{exe}
\ex \label{bsp:Stress} This coffee is not \textsc{hot}, it's \textsc{HOT}.
\end{exe}

\noindent The
intonational markedness hypothesis, as we will call it here, is then
an addition to the traditionalist's explanation of scalar implicatures
along the lines of the Gricean recipe. The crucial point is that under
this extra assumption, local readings are a marked phenomenon. If
supplemented with the intonational markedness hypothesis,
traditionalists would therefore predict that local readings are
available for \as- and \es-sentences, but only if intonationally
marked by contrastive stress; since this reading is marked, presumably
it would still be predicted to be dispreferred even if available.

@@

We are generally sympathetic towards
\citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
reinterpretation of the data, but note, as
\citet{ChemlaSpector2010:Experimental-Ev} already observed, that his
typicality-based explanation does not extend to \es-sentences in an
obvious way. Moreover, typicality itself is not a satisfactory
primitive in a putative explanation of the pragmatic use of
quantifiers. Plausibly, the reason why quantifier \emph{some} is more
typical for some set sizes than others is at least dependent on, if not
entirely derived from, its contrast with other conceivable
alternatives, e.g., numerals within the subitizing range, as well as
\emph{few}, \emph{most} or \emph{many}
\citep[c.f.][]{DegenTanenhaus2012:Processing-Scal}. For these reasons,
we believe that typicality and other pictorial effects need to be
taken seriously in the experimental design, but do not give a
satisfactory account of the observed variation all by themselves.

@@

\paragraph{Preference-related controls.} In order to test whether the
order of critical positions for different readings within a sequence
had an influence on responses, we included a second type of control
conditions. These conditions also controlled whether prosodic
information can, in principle, shift reading preferences in the
present task. Note that for our target sentences, the logical
entailment relations between readings always require local readings to
be evaluated at the end of a sequence. It could thus in principle be
possible that no subject ever reaches this point, because they gave
truth-value judgements earlier, thereby ending the trial. In that case
it would be unclear if these decisions have been affected by a general
unavailability of local readings or by the fact that one of the
earlier presented readings is the preferred one. By including globally
ambiguous structures with a known preference over available readings,
we thus intended to test whether participants in our task occasionally
choose dispreferred readings, even if they were available only at a
critical position following the preferred readings.

@@

\paragraph{Target conditions and positional controls}
Performance on positional controls was high (92\% correct responses on
average), indicating that subjects understood the task, giving
truth-value judgements at the right moment in a sequence without being
influenced in general by inessential features of the picture material
or showing general response biases.

The judgments obtained for the four target conditions are depicted in
Figure \ref{fig:JudgmentsK2}.\dn{we should introduce the actual
  sequences that we presented so that it is clear what it means to say
\emph{true} or \emph{false} on some position or other}
%
\begin{figure}[]
\centering
\subfloat[][\as-neutral]{
% \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
\begin{tikzpicture}[scale=0.8]

@@

The interaction of {\it Participant} and {\it Reading} shows that
there are indeed varying preferences for local readings among German
speakers (see Table~\ref{table:answer-types-as}).
%
\begin{table}[t]
  \centering
      \begin{tabular}{lccc}
      & \multicolumn{3}{c}{\es} \\ \cmidrule(r){2-4}
      \as & literalist & localist & incons. \\ \midrule
      literalist   & 19 & 2 & 6\\
      localist     &  0 & 7 & 0 \\
      incons. &  2 & 1 & 1\\
    \end{tabular}
    \caption{Contingency table showing the number of occurrences of
      \emph{response types} in the \as- and \es-conditions with
      neutral intonation. \emph{Literalists} are subjects who gave
      responses that were classified as either a literal response or
      an error; \emph{localist} are subjects who gave responses
      that were classified as either a 
      local response or an error. Subjects who gave at least two
      responses from different categories (literal, global, local) are
      classified as \emph{inconsistent}. (No subject's responses where
      errors exclusively and there where no \emph{globalists}, as
      defined in parallel fashion.)}
    \label{table:answer-types-as}
\end{table}
%
Further examination of the distribution of local readings revealed a
clear pattern (see Figure \ref{fig:HistogramLocalReadingsK2}). The
relative frequency of local judgments per participant strongly
correlated between all four conditions (all $r>.6, p<.001$). Appart
from the localists about half of the participants (and 41.5\% of all
participants) were consistently giving judgments that indicate literal
readings. Only a minority of participants exhibited
inconsistency. Reading preferences were more clear-cut in the
\as-conditions than in the \es-conditions. The number of consistent
literalists was lower in the \es-conditions (25.6\%) as compared to
the \as-conditions (57.3\%). Also, the number of participants that
showed inconsistency was higher in these conditions. However, the
number of consistent localists did hardly differ between
constructions.

@@

\subfloat[][\es-accented]{
\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_AKZ.jpg}
\label{fig:ReadingsAE}
}
\subfloat[][\es-neutral]{
\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_NTR.jpg}
\label{fig:ReadingsGE}
}
\label{fig:HistogramLocalReadingsK2}
\caption[]{Judgments for the four target conditions}
\end{figure}

The three way-interaction of {\it Participant}, {\it Construction} and
{\it Reading} is due to the fact that for some participants
preferences for local over other readings deviated between the two
construction types. These deviations were, however, not systematic to
any degree. How much local preferences deviated between the two
construction types per participant is depicted in Figure \ref{}. Most
participants had exactly the same preferences in the two
constructions. However, a few had a stronger and a few others a weaker
preference for local readings in the \es- than in the
\as-conditions. Since we did not find any systematic patterns
here, we speculate that the three-way interaction is due to the
\es-construction beeing understood non-standardly by a
few participants. This speculation is plausible given the higher
number of errors in the \es- as compared to the \as-conditions.

@@

\paragraph{Preference-related controls}

Participants' judgments are depicted in Figures \ref{Fig:EC_judgments}
and \ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if
they were as expected under one of these readings, and as "other" if
they were not. The distributions of readings thus coded is illustrated
in Figure \ref{fig:response-type-freque-TRF}.  Overall, participants
mainly gave answers corresponding to the \lc-reading (65\%).
Moreover, this pattern was constrained by prosody. When prosody
supported a dispreferred \ec-reading, the number of \ec-decisions were
increased and vice versa.

@@

\begin{figure}
\includegraphics[width=\textwidth]{../pictures/paper/graph_lc.pdf}
\caption{Judgments for prefence-related controls (LC sequence). Relative frequencies
of {\it yes/no} judgments is plotted against the position within the
trial. Each {\it LC sequences} consisted of seven pictures, in which the
critical positions for a reading were the third position ("true" corresponded
to an \lc reading) and the sixth position ("false" corresponded to an \ec reading)}
\label{Fig:LC_judgments}.
\end{figure}

@@

  \begin{axis}[ybar, 
               enlarge x limits=0.5,
               enlarge y limits=0.25, 
               legend style={at={(0.5,-0.15)},
                 anchor=north,
                 legend columns=-1}, 
               ylabel={\% of answers (rounded)}, 
               symbolic x coords={neutral,LC-pref,EC-pref}, 
               xtick=data,
               nodes near coords,
               nodes near coords align={vertical},
               x = 45, 
               bar width = 3mm,
               ymin = 8
               ]

@@

  \begin{axis}[ybar, 
               enlarge x limits=0.5, 
               enlarge y limits=0.25, 
               legend style={at={(0.5,-0.15)},
                 anchor=north,
                 legend columns=-1}, 
               % ylabel={\% of answers}, 
               symbolic x coords={neutral,LC-pref,EC-pref}, 
               xtick=data,
               nodes near coords,
               nodes near coords align={vertical},
               x = 45, 
               bar width = 3mm,
               ymin = 8
               ]

@@

\subsection{Summary \& Interpretation}
\label{sec:interpretation}

High scores of success clearly indicate that participants understood 
the incremental verification task and were in general able to give 
judgements at the earliest possible point in a picture sequence. 
Moreover, results obtained for the preference-related controls  
show that our design is able to detect multiple readings and preferences 
among these. Crucially, the amount of response types for \lc- and \ec-readings 
reflected the known preference for the former, \emph{irrespective} of the 
order in which each reading could first be judged in a given sequence.
Finally, the incremental verification task was generally sensitive
to prosody. However, prosodic effects were restricted to the preference-related 
controls. As expected, in these conditions, the dispreferred \ec-reading was chosen 
significantly more often when supported by prosodic phrasing. Interestingly, 
contrastively accenting scalar \emph{some} had no effect on the observed 
decisions in the target conditions. Crucially, local readings occurred in both
\as- and \es-sentences, independently of prosody. Finally, closer examination of 
the participants' decisions revealed two groups: participants in the first
group consistently gave answers corresponding to local readings, whereas participants
in the second group consistently showed a literal interpretation.

@@

\subsection{General Discussion}
\label{sec:discussion}

There are a number of conceivable objections to our interpretation of
the presented results. We will consider the most pressing ones in the
following and conclude that the main point raised above remains valid:
neither traditionalism, nor grammaticalism is able to account for the
present pattern of results.

@@

There are two kinds of reply to this objection (and others like
it). Firstly, it is true that we cannot conclude with certainty that
our data implies that (\ref{bsp:observed-preferences}) is the actual
preference relation among candidate readings of our target
sentences. But that does not matter. Even if the observed distribution
has nothing to do with preferences over readings, the main point
remains that neither traditionalism nor grammaticalism predicts the
observed distribution of responses. Secondly, even if we assume that
the incremental verification task is incapable of indicating
preferences among pragmatic readings of the relevant kind, then it
should at least be able to indicate availability of readings. So if
we deny the observed response patterns the power to indicate
preference, what should the information about availability of readings
be that we may safely infer from it? It should be that local readings
are available and that global readings are not. But that is again not
predicted by either traditionalism or grammaticalism. The former cannot
explain the substantial number of local responses, the latter doesn't
explain the absence of global responses.

>>>>

\begin{abstract}
  Scalar item \emph{some} is widely assumed to readily undergo a
  pragmatic meaning enrichment to \emph{some but not all} if it occurs
  in matrix position. The question under which circumstances this
  meaning enrichment can take place in embedded position is an
  important one to decide the delineation between semantics and
  pragmatics, and therefore currently under renewed debate. % Some claim
  % that it requires marked intonation for the relevant pragmatic
  % enrichment to occur in embedded position; others allow for it more
  % freely.
  We present a novel experimental paradigm to test whether so-called
  local readings are available with or without prosodic markedness. On
  top of adding prosodic manipulation, our experimental design was
  catered to a number of methodological difficulties that were
  identified for previous studies, such as the possibility of
  confounds of pictorial properties. The data obtained refutes both a
  traditional Gricean view of scalar implicature calculation, as well
  as the more recent grammatical approach.
\end{abstract}

@@

Although strictly speaking not a part of a Gricean theory of scalar
implicature calculation, traditionalists frequently concede that local
readings are in principle available, albeit not as a standard scalar
implicature, but as a different pragmatic process triggered by
prosodic markedness. We examine this \emph{intonational markedness
  hypothesis} separately in Section~\ref{sec:inton-mark-hypoth},
alongside a brief revision of the relevant experimental data.

@@

Consequently, the \mymark{Gricean recipe}
\citep[c.f.][]{Geurts2010:Quantity-Implic} for deriving a simple
scalar inference like that in (\ref{bsp:Plain-SI-Implicature}) from an
utterance of (\ref{bsp:Plain-SI-Target}) is as follows: if the issue
whether Hans solved only some or all of the problems is relevant, then
a cooperative and knowledgable speaker would utter
(\ref{bsp:Plain-SI-Alternative}) if in a position to do so; hence, one
of the most natural explanations of why such a speaker has not uttered
(\ref{bsp:Plain-SI-Alternative}), but only (\ref{bsp:Plain-SI-Target})
is that she is uncertain of whether (\ref{bsp:Plain-SI-Alternative})
is true; but on the assumption that she is knowledgeable (competent,
opinionated, informed \dots) it follows that
(\ref{bsp:Plain-SI-Implicature}) should in fact be true.\fn{We are
  glossing here somewhat swiftly over the more nuanced details of the
  derivation of implicatures targeting the speaker's epistemic state
  \citep[e.g.][]{Gazdar1979:Pragmatics:-Imp,Soames1982:How-Presupposit},
  as this is not crucially relevant for the issues we are interested
  in here.}

@@

Taking stock, traditionalism and grammaticalism predict different
patterns of availability and preference for \as- and
\es-sentences. Most notably, traditionalism does not predict local
readings for \es-sentences to be available. Grammaticalism predicts
that all readings are available, but, given the strongest meaning
hypothesis, also comes with a clear indication of preference: literal
meanings are dispreferred. All predictions are summarized in
Table~\ref{tab:predictions}.

@@

\subsection{The Intonational Markedness Hypothesis}
\label{sec:inton-mark-hypoth}

Although traditionalism does not of itself predict local readings to
be available, many authors who adhere to a traditionalist position
maintain that local readings are available if and only if the
embedded scalar item is intonationally marked by contrastive stress
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Scalar-expressi}. This
is taken to be continuous with other cases where pragmatic enrichments
can take scope under logical operators if and only if the relevant
focal accent is present (\ref{bsp:Stress}).

\begin{exe}
\ex \label{bsp:Stress} This chili is not \textsc{spicy}, it's \textsc{SPICY}.
\end{exe}

\noindent The \emph{intonational markedness hypothesis}, as we will
call it here, is then an addition to the traditionalist's explanatory
repertoire. The crucial point is that under this extra assumption,
local readings are a marked phenomenon, and not the product of the
same process as run-of-the-mill scalar implicatures associated with
scalar items in matrix position. If supplemented with the intonational
markedness hypothesis, traditionalists would therefore predict that
local readings are available for \as- and \es-sentences, but only if
intonationally marked by contrastive stress; since this reading is
marked, presumably it would still be predicted to be dispreferred even
if available.

@@

We are generally sympathetic towards
\citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
reinterpretation of the data, but note, as
\citet{ChemlaSpector2010:Experimental-Ev} already observed, that his
typicality-based explanation does not extend to \es-sentences in an
obvious way. Moreover, typicality itself is not a satisfactory
primitive in a putative explanation of the use of
quantifiers. Plausibly, the reason why quantifier \emph{some} is more
typical for some set sizes than others is at least dependent on, if
not entirely derived from, its contrast with other conceivable
alternatives, e.g., numerals within the subitizing range, as well as
\emph{few}, \emph{most} or \emph{many}
\citep[c.f.][]{DegenTanenhaus2012:Processing-Scal}. For these reasons,
we believe that typicality and other pictorial effects need to be
taken seriously in the experimental design, but do not give a
satisfactory account of the observed variation all by themselves.

@@

\paragraph{Preference-related controls.} In order to test whether the
order of critical positions for different readings within a sequence
had an influence on responses, we included a second type of control
conditions. Secondly, these controls served as a test whether the
incremental verification task could possibly detect at least ordinal
preference relations among multiple candidate readings. Finally, these
conditions also controlled whether prosodic information can, in
principle, shift answer patterns in the present task. Note that for
our target sentences, the logical entailment relations between
readings always require local readings to be evaluated at the end of a
sequence. It could thus in principle be possible that no subject ever
reaches this point, because they gave truth-value judgements earlier,
thereby ending the trial. In that case it would be unclear if these
decisions have been affected by a general unavailability of local
readings or by the fact that one of the earlier presented readings is
the preferred one. By including globally ambiguous structures with a
known preference over available readings, we thus intended to test
whether participants in our task occasionally choose dispreferred
readings, even if they were available only at a critical position
following the preferred readings.

@@

\paragraph{Target conditions and positional controls.}
Performance on positional controls was high (92\% correct responses on
average), indicating that subjects understood the task, giving
truth-value judgements at the right moment in a sequence without being
influenced in general by inessential features of the picture material
or showing general response biases.

The judgments obtained for the four target conditions are depicted in
Figure \ref{fig:JudgmentsK2}.
%
\begin{figure}[]
\centering
\subfloat[][\as-neutral]{
% \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
\begin{tikzpicture}[scale=0.8]

@@

The interaction of {\it Participant} and {\it Reading} shows that
there are indeed varying preferences for local readings among German
speakers (see Table~\ref{table:answer-types-as}).
%
\begin{table}[t]
  \centering
      \begin{tabular}{lccc}
      & \multicolumn{3}{c}{\es} \\ \cmidrule(r){2-4}
      \as & literalist & localist & incons. \\ \midrule
      literalist   & 19 & 2 & 6\\
      localist     &  0 & 7 & 0 \\
      incons. &  2 & 1 & 1\\
    \end{tabular}
    \caption{Contingency table showing the number of occurrences of
      \emph{response types} in the \as- and \es-conditions with
      neutral intonation. \emph{Literalists} are subjects who gave
      responses that were classified as either a literal response or
      an error; \emph{localist} are subjects who gave responses
      that were classified as either a 
      local response or an error. Subjects who gave at least two
      responses from different categories (literal, global, local) are
      classified as \emph{inconsistent}. (No subject's responses where
      errors exclusively and there where no \emph{globalists}, as
      defined in parallel fashion.)}
    \label{table:answer-types-as}
\end{table}
%
Further examination of the distribution of local readings revealed a
clear pattern (see Figure~\ref{fig:HistogramLocalReadingsK2}). The
relative frequency of local judgments per participant strongly
correlated between all four conditions (all $r>.6, p<.001$). Appart
from the localists about half of the participants (41.5\% of all
participants)\dn{is this ``about half''?} were consistently giving
judgments that indicate literal readings. Only a minority of
participants exhibited inconsistency. Reading preferences were more
clear-cut in the \as-conditions than in the \es-conditions. The number
of consistent literalists was lower in the \es-conditions (25.6\%) as
compared to the \as-conditions (57.3\%). Also, the number of
participants that showed inconsistency was higher in these
conditions. However, the number of consistent localists did hardly
differ between constructions.

@@

\subfloat[][\es-accented]{
\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_AKZ.jpg}
\label{fig:ReadingsAE}
}
\subfloat[][\es-neutral]{
\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_NTR.jpg}
\label{fig:ReadingsGE}
}
\caption[]{Judgments for the four target conditions}
\label{fig:HistogramLocalReadingsK2}
\end{figure}

The three way-interaction of {\it Participant}, {\it Construction} and
{\it Reading} is due to the fact that for some participants
preferences for local over other readings deviated between the two
construction types. These deviations were, however, not systematic to
any degree. How much local preferences deviated between the two
construction types per participant is depicted in Figure
\ref{}.\dn{INCLUDE RELEVANT GRAPH!} Most
participants had exactly the same preferences in the two
constructions. However, a few had a stronger and a few others a weaker
preference for local readings in the \es- than in the
\as-conditions. Since we did not find any systematic patterns
here, we speculate that the three-way interaction is due to the
\es-construction beeing understood non-standardly by a
few participants. This speculation is plausible given the higher
number of errors in the \es- as compared to the \as-conditions.

@@

\paragraph{Preference-related controls.} Participants' judgments are
depicted in Figures \ref{Fig:EC_judgments} and
\ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if they
were as expected under one of these readings, and as "other" if they
were not. The distributions of readings thus coded is illustrated in
Figure \ref{fig:response-type-freque-TRF}.  Overall, participants
mainly gave answers corresponding to the \lc-reading (65\%).
Moreover, this pattern was constrained by prosody. When prosody
supported a dispreferred \ec-reading, the number of \ec-decisions were
increased and vice versa.

@@

\begin{figure}
\includegraphics[width=\textwidth]{../pictures/paper/graph_lc.pdf}
\caption{Judgments for prefence-related controls (LC sequence). Relative frequencies
of {\it yes/no} judgments is plotted against the position within the
trial. Each {\it LC sequences} consisted of seven pictures, in which the
critical positions for a reading were the third position ("true" corresponded
to an \lc reading) and the sixth position ("false" corresponded to an \ec reading).}
\label{Fig:LC_judgments}
\end{figure}

@@

  \begin{axis}[ybar, 
               enlarge x limits=0.45,
               enlarge y limits=0.25, 
               legend style={at={(0.5,-0.15)},
                 anchor=north,
                 legend columns=-1}, 
               ylabel={\% of answers (rounded)}, 
               symbolic x coords={neutral,LC-pref,EC-pref}, 
               xtick=data,
               nodes near coords,
               nodes near coords align={vertical},
               x = 45, 
               bar width = 3mm,
               ymin = 8
               ]

@@

  \begin{axis}[ybar, 
               enlarge x limits=0.45, 
               enlarge y limits=0.25, 
               legend style={at={(0.5,-0.15)},
                 anchor=north,
                 legend columns=-1}, 
               % ylabel={\% of answers}, 
               symbolic x coords={neutral,LC-pref,EC-pref}, 
               xtick=data,
               nodes near coords,
               nodes near coords align={vertical},
               x = 45, 
               bar width = 3mm,
               ymin = 8
               ]

@@

\subsection{Discussion}
\label{sec:discussion-1}

\paragraph{Summary \& Interpretation.} High scores of success clearly
indicate that participants understood the incremental verification
task and were in general able to give judgements at the earliest
possible point in a picture sequence.  Moreover, results obtained for
the preference-related controls show that our design is able to detect
multiple readings and preferences among these. Crucially, the amount
of response types for \lc- and \ec-readings reflected the known
preference for the former, \emph{irrespective} of the order in which
each reading could first be judged in a given sequence.  Finally, the
incremental verification task was generally sensitive to
prosody. However, prosodic effects were restricted to the
preference-related controls. As expected, in these conditions, the
dispreferred \ec-reading was chosen significantly more often when
supported by prosodic phrasing. Interestingly, contrastively accenting
scalar \emph{some} had no effect on the observed decisions in the
target conditions. Crucially, local readings occurred in both \as- and
\es-sentences, independently of prosody. Finally, closer examination
of the participants' decisions revealed two groups: participants in
the first group consistently gave answers corresponding to local
readings, whereas participants in the second group consistently showed
a literal interpretation.

@@

\paragraph{Some Potential Objections.} There are a number of
conceivable objections to our interpretation of the presented
results. We will consider the most pressing ones in the following and
conclude that the main point raised above remains valid: neither
traditionalism, nor grammaticalism is able to account for the present
pattern of results.

@@

Although we cannot rule out that the incremental verification task
detects preferences among multiple readings only for some sources of
variability in readings and not others, it is by no means clear why it
should not. The burden of argument is on the sceptic. But even if we
assume that the incremental verification task is incapable of reliably
indicating preferences among candidate pragmatic enrichments of the
relevant kind, then it should at least be able to indicate
availability of readings. So if we deny the observed response patterns
the power to indicate preference, what should the information about
availability of readings be that we may safely infer from it? It
should be that local readings are available and that global readings
are not. But that is not predicted by either traditionalism or
grammaticalism. The former cannot explain the substantial number of
local responses, the latter doesn't explain the absence of global
responses.
